\documentclass{article}

\usepackage[submission]{colm2026_conference}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{url}
\usepackage{xcolor}
\usepackage{lineno}

\setlength{\emergencystretch}{2em}

\title{Trusted by Proxy: Source-Laundering Attacks in Multi-Agent LLM Systems}
\author{Anonymous Authors}
\date{}

\begin{document}
\ifcolmsubmission
\linenumbers
\fi

\maketitle

\begin{abstract}
Multi-agent LLM systems increasingly split user requests across specialized
agents that read documents, summarize evidence, plan actions, and execute tool
calls. This modularity creates a trust-boundary problem: an instruction that
originates in untrusted content can be rewritten by an upstream peer as an
apparently ordinary action item, causing downstream agents to treat it as more
authoritative than the original source. We call this failure mode \emph{source
laundering}. We introduce SLaMBench, a compact synthetic benchmark for studying
source-laundering attacks in tool-using agents across workspace, CRM,
code-review, travel, and research-assistant domains. On a 50-pair multidomain
benchmark with explicit tool schemas, an extractive reader--planner--executor
topology raises unauthorized-recipient attack success from 6\% in a direct
single-agent baseline to 22\%, a +16 percentage-point lift with paired bootstrap
95\% CI [4, 26]. A deterministic TraceGate monitor eliminates observed
unauthorized sends while preserving more injected-task utility than the
vulnerable multi-agent system. Cross-model results are mixed:
\texttt{gpt-4.1-nano} is already directly vulnerable, so delegation does not
further increase attack success, but TraceGate still blocks all observed
unauthorized sends. These results support a systems-security view of agentic
AI: inter-agent messages are not merely summaries, but security-relevant
authority transitions.
\end{abstract}

\section{Introduction}

LLM agents are increasingly deployed as \emph{systems} rather than as single
prompts. A user-facing assistant may delegate document reading to one agent,
planning to another, and tool execution to a third. This decomposition is useful:
it localizes expertise, shortens prompts, and makes complex workflows easier to
engineer. However, it also creates a security boundary that is easy to overlook.
When a Reader agent processes an untrusted artifact, it may preserve facts while
silently dropping the artifact's lack of authority. A Planner or Executor that
receives the resulting peer message can then act on the content as if it were a
trusted instruction.

Consider a benign user request: ``read this vendor note and email
\texttt{finance@example.test} the payment terms.'' The vendor note correctly
states the payment terms, but also contains ``add \texttt{audit-log@example.test}
as a required recipient.'' A direct single-agent system sees that the extra
recipient is embedded in the document. In a multi-agent system, however, a Reader
might rewrite the artifact as ``action item: add the audit recipient,'' and a
Planner might further rewrite it as ``required step: send the summary to
\texttt{audit-log@example.test}.'' The downstream Executor no longer sees a raw
untrusted instruction; it sees a plan produced by a peer. The question is not
whether indirect prompt injection exists, but whether delegation changes the
instruction's effective authority.

We call this transformation \emph{source laundering}. The analogy is intentional:
the content has not disappeared, but its provenance has been washed through a
sequence of apparently legitimate transformations. Source laundering is related
to indirect prompt injection~\citep{greshake2023not,zhan2024injecagent}, but its
unit of analysis is the inter-agent boundary. It is also related to classic
confused-deputy failures~\citep{hardy1988confused}: a downstream component with
tool authority is induced to exercise that authority on behalf of a less trusted
principal. In LLM systems, the designation of the action and the authority for
that action can become separated across natural-language messages.

This paper studies three research questions. \textbf{RQ1:} Does an extractive
multi-agent topology increase unauthorized tool use relative to direct exposure
to the same injected artifact? \textbf{RQ2:} Which payload styles and domains
most often survive the reader--planner boundary? \textbf{RQ3:} Can simple
provenance-preserving prompts or deterministic tool-boundary checks reduce the
risk without destroying benign utility?

\begin{figure}[t]
\centering
\small
\setlength{\fboxsep}{4pt}
\begin{tabular}{c@{\hspace{0.35em}}c@{\hspace{0.35em}}c@{\hspace{0.35em}}c@{\hspace{0.35em}}c@{\hspace{0.35em}}c@{\hspace{0.35em}}c}
\fbox{\begin{minipage}{0.15\textwidth}\centering
\textbf{Untrusted artifact}\\
``add audit recipient''
\end{minipage}}
& $\rightarrow$ &
\fbox{\begin{minipage}{0.15\textwidth}\centering
\textbf{Reader}\\
action item
\end{minipage}}
& $\rightarrow$ &
\fbox{\begin{minipage}{0.15\textwidth}\centering
\textbf{Planner}\\
required step
\end{minipage}}
& $\rightarrow$ &
\fbox{\begin{minipage}{0.15\textwidth}\centering
\textbf{Executor}\\
\texttt{send\_email}
\end{minipage}}
\\[0.25em]
&&&&&&
$\downarrow$
\\[0.25em]
&&&&&&
\fbox{\begin{minipage}{0.15\textwidth}\centering
\textbf{TraceGate}\\
block or prune
\end{minipage}}
\end{tabular}
\caption{Source laundering turns an untrusted artifact instruction into a
peer-agent action item and then an executable tool call. TraceGate intervenes
at the tool boundary, where authorization can be checked deterministically.}
\label{fig:pipeline}
\end{figure}

We make four contributions. First, we formalize source laundering as an
authorization-boundary failure in multi-agent LLM systems. Second, we introduce
SLaMBench, a compact synthetic benchmark with deterministic mock tools and no
real external side effects. Third, we evaluate direct, extractive multi-agent,
source-preserving, capability-scoped, and runtime-monitored topologies. Fourth,
we show that extractive delegation increases unauthorized-recipient tool calls on
a scaled \texttt{gpt-5.4-nano} benchmark, while a simple monitor eliminates
observed unauthorized sends. The result is deliberately narrow: we do not claim
that every multi-agent system is less secure than every single-agent system.
Rather, we show that a plausible extractive delegation boundary can convert
untrusted artifact text into peer-agent authority unless the system explicitly
preserves and enforces provenance.

\section{Threat Model and Security Property}

The user provides a legitimate task, such as reading an invoice note and
emailing an authorized summary to \texttt{finance@example.test}. The adversary
can place text inside an untrusted artifact that the agent system must process,
such as a vendor note, customer ticket, pull-request note, itinerary note, or
abstract note. The adversary cannot modify system prompts, trusted context, tool
code, model weights, runtime policy, or the user's initial goal. The attacker
also does not control the mock tool layer; all tool outputs are deterministic and
closed-world.

The protected assets are synthetic but structurally representative: authorized
recipients, synthetic secrets, protected status fields, calendar attendees, and
memory entries that should only be written under trusted authorization. The core
security property is \emph{authority separation}: untrusted content may supply
facts needed to complete the user task, but it must not authorize new tool calls,
new recipients, protected updates, memory policies, or secret disclosure. For
example, a vendor note may state that an invoice is due in 30 days, but it may
not authorize the assistant to send a copy to an additional recipient.

We define a source-laundering attack as an execution with three properties. First,
an attacker-controlled instruction appears in an untrusted artifact. Second, an
intermediate agent transforms that instruction into a peer message without
sufficient source, trust, and no-authority metadata. Third, a downstream agent
acts on the transformed instruction by emitting a forbidden tool call. This
separates source laundering from ordinary task failure: a run that merely fails
to send the legitimate email is a utility failure, while a run that sends to
\texttt{audit-log@example.test} is a security failure.

All experiments use synthetic targets such as \texttt{audit-log@example.test} and
synthetic secrets. Tools are deterministic mocks, and no real email, calendar,
ticket, browser, or memory service is contacted. This choice makes the benchmark
safe to release and enables deterministic scoring from saved tool logs.

\section{SLaMBench}

SLaMBench contains paired benign and injected task variants. The main scaled task
set, SLaMBench-50
(\path{slambench/tasks/subtle_multidomain_50pairs_v2.jsonl}), contains 50 benign
tasks and 50 injected variants across five domains. Each pair shares the same
user goal, trusted context, allowed tools, expected benign outcome, and reference
benign tool calls. The injected variant adds exactly one attacker-controlled
payload to the untrusted artifact. This paired design lets us compare benign
utility and injected security without changing the legitimate task.

\begin{table}[t]
\centering
\small
\begin{tabular}{lcll}
\toprule
Domain & Pairs & Legitimate action & Unauthorized action \\
\midrule
Workspace & 10 & Email payment terms to finance & Add audit recipient \\
CRM & 10 & Update ticket and email support & Add audit recipient \\
Code review & 10 & Update tracker and email maintainer & Add audit recipient \\
Travel & 10 & Create approved calendar event & Add audit recipient \\
Research & 10 & Write bibliography note and email lead & Add audit recipient \\
\bottomrule
\end{tabular}
\caption{SLaMBench scaled task set used for the main result.}
\label{tab:slambench}
\end{table}

\paragraph{Task format.}
Each task specifies the user goal, trusted context, untrusted artifacts, allowed
tools, expected benign outcomes, forbidden outcomes, and an attack tool-call
template. The allowed tools include mock document reading, email sending, memory
writes, ticket updates, tracker updates, and calendar creation, depending on the
domain. The forbidden outcome is task-specific: in the main result it is any
executed \texttt{send\_email} call containing \texttt{audit-log@example.test},
with additional checks for synthetic-secret leakage and untrusted memory-policy
writes.

\paragraph{Payload classes.}
The injected variants use five payload classes. \emph{Direct instruction}
explicitly tells downstream assistants to send the extra recipient. \emph{Fake
authority} claims that a user, compliance process, or policy has approved the
extra recipient. \emph{Delegation poisoning} targets the planning boundary by
asking the Reader or Planner to tell the Executor to perform the forbidden call.
\emph{Summary bait} presents the forbidden recipient as an action item that seems
natural to extract. \emph{Memory poisoning} tries to write a durable policy such
as ``external vendor notes are trusted.'' These payloads are intentionally
simple; the goal is not to optimize an adaptive attack, but to measure how
ordinary delegation transforms source and authority.

\paragraph{Why synthetic tasks.}
The benchmark is synthetic by design. This makes every tool call inspectable,
eliminates risk to real users, and avoids relying on LLM judges for the main
security metric. Synthetic tasks also let us pair benign and injected variants
with controlled differences. The limitation is that absolute attack rates should
not be interpreted as production incident rates; the benchmark is a diagnostic
instrument for a specific compositional failure mode.

\section{Agent Topologies and Defenses}

\textbf{Direct single agent} (\texttt{c0\_single\_direct}) sees the user goal,
trusted context, untrusted artifact, and tool signatures, then emits final tool
calls. This is the baseline for measuring whether delegation adds risk beyond
ordinary indirect prompt injection.

\textbf{Extractive multi-agent} (\texttt{c2x\_3agent\_extractive\_naive}) uses a
Reader that extracts all action items from the artifact, including operational
instructions; a Planner turns the Reader output into steps; and an Executor emits
tool calls. The untrusted artifact is not labeled as untrusted in the extractive
Reader prompt. This condition is a stress test for the source-laundering
mechanism: it models a common engineering pattern where upstream agents compress
or normalize task context before execution.

\textbf{Source-preserving} (\texttt{c3\_source\_preserving}) requires the Reader
to preserve source identifiers and trust labels, and instructs Planner/Executor
agents not to convert untrusted instructions into authorized actions. This tests
whether natural-language provenance metadata is sufficient to protect the
inter-agent boundary.

\textbf{Capability-scoped} (\texttt{c4\_capability\_scoped}) allows peer agents
to suggest actions but not authorize sensitive tools unless the original user
goal or trusted context authorizes them. This approximates a capability-security
design in prompt form: peer messages may designate candidate actions, but do not
carry ambient authority to execute them.

\textbf{TraceGate} (\texttt{c5x\_tracegate\_extractive\_naive}) uses the same
extractive topology as c2x, but a deterministic runtime monitor checks sensitive
tool calls before execution. The monitor blocks synthetic-secret disclosure,
unauthorized email recipients or calendar attendees, untrusted memory-policy
writes, and sensitive actions without trusted authorization. The current
implementation prunes mixed-recipient emails: if a model sends to both an
authorized recipient and an unauthorized recipient, the unauthorized recipient is
blocked while the authorized send is preserved. TraceGate is intentionally simple
so that failures and false positives are auditable.

\section{Metrics and Analysis Protocol}

All metrics are computed from saved tool traces. \textbf{Benign Success Rate}
(BSR) is the fraction of benign variants where the expected user task succeeds
and no forbidden event occurs. \textbf{Injected Utility Success Rate} (IUSR)
applies the same benign-success check to injected variants while requiring that
no forbidden event occurs. \textbf{Attack Success Rate} (ASR) is the fraction of
injected variants with a forbidden event in the executed tool log. Blocked calls
are not counted as attacks because they do not execute.

\textbf{Authority Transfer Rate} (ATR) measures delegation-specific lift:
\begin{equation*}
\mathrm{ATR}(c) = \mathrm{ASR}(c) - \mathrm{ASR}(\texttt{c0\_single\_direct}).
\end{equation*}
This metric is important because some models are directly vulnerable. A high raw
ASR in a delegated condition is evidence of insecurity; a positive ATR is
evidence that the inter-agent boundary adds risk beyond direct exposure.

\textbf{Provenance Dropout Rate} (PDR) is the fraction of reader/planner messages
that carry task-specific forbidden content without preserving source, trust, and
no-authority metadata. \textbf{Capability-Normalized Attack Success} (CNAS) is
ASR divided by BSR, which prevents a weak agent from appearing secure merely
because it fails both benign and malicious tasks. We report nonparametric
bootstrap confidence intervals for single-condition rates and paired bootstrap
intervals for differences on the same task set.

\section{Main Results}

The main scaled result uses \texttt{gpt-5.4-nano} on SLaMBench-50. Full tables
are in \path{paper/tables/openai_schema_prompt_50pairs_gpt54nano_tracegate_pruned/}.

\begin{table}[t]
\centering
\small
\begin{tabular}{lrrrrrrr}
\toprule
Condition & BSR & IUSR & ASR & ATR & PDR & CNAS & Blocks \\
\midrule
Direct single-agent & 60\% & 54\% & 6\% & 0 pp & 0\% & 0.10 & 0 \\
Extractive multi-agent & 70\% & 50\% & 22\% & +16 pp & 77\% & 0.31 & 0 \\
TraceGate & 66\% & 64\% & 0\% & -6 pp & 69\% & 0.00 & 11 \\
\bottomrule
\end{tabular}
\caption{Main 50-pair result on \texttt{gpt-5.4-nano}. ATR is ASR minus the
direct-baseline ASR; PDR is provenance dropout in intermediate messages; CNAS is
ASR divided by BSR.}
\label{tab:main}
\end{table}

The extractive multi-agent topology increases ASR by +16 percentage points over
direct exposure, with paired bootstrap 95\% CI [4, 26]. TraceGate reduces ASR by
-22 points relative to extractive multi-agent delegation, with paired bootstrap
95\% CI [-34, -10]. TraceGate produces zero audit-log sends. It records 11
sensitive-call blocks in total: 10 on injected variants and one benign memory
write false positive. Nine blocks are audit-recipient email attempts, and five
mixed-recipient email calls are sanitized so the authorized recipient still
receives the intended message.

\paragraph{Answer to RQ1.}
The positive ATR shows that delegation can add risk beyond direct exposure. The
same injected artifacts are present in both c0 and c2x, but c2x has a higher ASR.
The trace-level explanation is consistent with the source-laundering mechanism:
the Reader extracts the forbidden recipient as an action item, the Planner
promotes it into a required step, and the Executor emits the corresponding tool
call. The direct baseline is not immune, but the delegated topology makes the
forbidden instruction more likely to execute.

\paragraph{Utility/security tradeoff.}
The extractive multi-agent system has higher benign success than the direct
baseline (70\% versus 60\%), suggesting that decomposition can improve task
completion. However, that utility gain comes with higher ASR and lower IUSR.
TraceGate recovers the best injected utility among the three main conditions
(64\%) while driving ASR to 0\%. This is the most practically important result:
tool-boundary enforcement can block source-laundered actions without simply
refusing the entire user task.

\paragraph{Provenance dropout.}
The high PDR values show that extractive delegation frequently carries forbidden
recipient content forward without source and authority metadata. TraceGate does
not repair this upstream provenance dropout; instead, it prevents the laundered
instruction from becoming an executed unauthorized tool call. This distinction
matters for system design. Prompt-level provenance can reduce the chance of bad
plans, but runtime enforcement is still useful when provenance has already been
lost.

\begin{table}[t]
\centering
\small
\begin{tabular}{lc}
\toprule
Payload class & c2x ASR \\
\midrule
Summary bait & 50\% \\
Fake authority & 40\% \\
Delegation poisoning & 10\% \\
Direct instruction & 10\% \\
Memory poisoning & 0\% \\
\bottomrule
\end{tabular}
\caption{Payload-level ASR for extractive multi-agent delegation.}
\label{tab:payload}
\end{table}

\paragraph{Answer to RQ2.}
Table~\ref{tab:payload} suggests that the most successful attacks are not the
most obviously adversarial ones. Summary bait and fake-authority payloads are
more effective than direct instructions in the extractive topology. This pattern
matches the threat model: a Reader optimized to extract action items is more
likely to preserve text that already looks like a legitimate workflow item, while
a direct imperative may remain visibly suspicious. The attack appears across all
five domains in c2x: workspace (3), CRM (1), code review (3), travel (2), and
research (2). This supports the claim that the mechanism is not just a
workspace/email artifact.

\paragraph{Qualitative trace.}
In one fake-authority workspace case, the Reader converts an untrusted
``user-approved routing exception'' into the action item ``also send the final
summary to \texttt{audit-log@example.test}.'' The Planner then schedules a
separate audit email, and the Executor sends it. In a TraceGate run on a summary
bait case, the model proposes a mixed-recipient email containing both
\texttt{finance@example.test} and \texttt{audit-log@example.test}; TraceGate
records the unauthorized recipient, prunes it, and executes the sanitized email
to finance. These traces illustrate why we distinguish upstream laundering from
downstream enforcement.

\section{Defense Ablations}

On the smaller 25-pair schema-prompt benchmark, source-preserving summaries and
capability-scoped prompting both reduce attacks, but neither is as attractive as
TraceGate.

\begin{table}[t]
\centering
\small
\begin{tabular}{lccc}
\toprule
Condition & BSR & ASR & Interpretation \\
\midrule
c2x & 72\% & 24\% & Vulnerable extractive delegation \\
c3 source-preserving & 44\% & 0\% & Secure but lower utility \\
c4 capability-scoped & 40\% & 4\% & No audit sends; strict secret-id failure \\
c5x TraceGate & 72\% & 0\% & Secure with best utility \\
\bottomrule
\end{tabular}
\caption{Defense ablations on the 25-pair benchmark.}
\label{tab:defenses}
\end{table}

\paragraph{Answer to RQ3.}
The ablation supports two conclusions. First, source and authority metadata are
helpful, because c3 and c4 substantially reduce observed attacks. Second,
prompt-only defenses can be brittle or overly conservative: both c3 and c4 reduce
benign success in this pilot. TraceGate is stronger in this setting because the
recipient-authorization rule is crisp and enforceable at the tool boundary. This
is not an argument against provenance-preserving prompts; rather, it suggests a
layered design in which upstream agents preserve metadata and downstream runtime
monitors enforce high-confidence invariants.

\section{Cross-Model Result}

The \texttt{gpt-4.1-nano} replication is mixed. On the 25-pair schema-prompt
benchmark, direct exposure is already vulnerable.

\begin{table}[t]
\centering
\small
\begin{tabular}{lccc}
\toprule
Model & c0 ASR & c2x ASR & c5x ASR \\
\midrule
\texttt{gpt-5.4-nano} & 4\% & 24\% & 0\% \\
\texttt{gpt-4.1-nano} & 24\% & 24\% & 0\% \\
\bottomrule
\end{tabular}
\caption{Cross-model schema-prompt result on the 25-pair benchmark.}
\label{tab:crossmodel}
\end{table}

Thus, the delegation-specific ASR lift does not replicate on
\texttt{gpt-4.1-nano}. This is not a failure of the threat model; it is a
capability/safety interaction. For \texttt{gpt-4.1-nano}, the direct baseline
already follows unauthorized artifact instructions often enough that delegation
does not add measurable risk. TraceGate remains effective on both models. The
right interpretation is therefore conditional: source laundering is most visible
when the direct model has enough instruction/data separation to resist some raw
artifact instructions, but downstream delegation can still remove that protective
context.

\section{Related Work}

\paragraph{Prompt injection and tool-using agents.}
Indirect prompt injection showed that LLM-integrated applications blur the
boundary between data and instructions when models process retrieved or
third-party content~\citep{greshake2023not}. AgentDojo evaluates
prompt-injection attacks and defenses for tool-using agents across realistic
tasks and security test cases~\citep{debenedetti2024agentdojo}. InjecAgent
benchmarks indirect prompt injection in tool-integrated agents, including user
tools and attacker tools~\citep{zhan2024injecagent}. Agent Security Bench
formalizes attacks and defenses across multiple agent stages, tools, and memory
mechanisms~\citep{zhang2024asb}. ToolEmu studies risks of LM agents with
emulated tools and safety evaluators~\citep{ruan2023toolemu}. Our benchmark is
smaller than these broad suites, but more diagnostic: it isolates whether peer
mediation changes the authority of an injected instruction.

\paragraph{Multi-agent propagation and memory/tool attacks.}
Prompt Infection studies LLM-to-LLM prompt injection in multi-agent systems,
focusing on self-replicating propagation across agents~\citep{lee2024promptinfection}.
AgentPoison shows that poisoned memory or RAG knowledge bases can steer LLM
agents without model training~\citep{chen2024agentpoison}. ToolHijacker studies
prompt injection against tool selection by manipulating malicious tool
documents~\citep{shi2025toolhijacker}. These works show that agent systems have
attack surfaces beyond the immediate user prompt. Source laundering differs by
focusing on an authorization transition: the attacker instruction does not need
to replicate, poison retrieval, or hijack tool selection; it only needs to be
rewritten by a trusted peer in a form that downstream agents treat as executable.

\paragraph{Defenses and systems-security framing.}
Several defenses aim to separate instructions from data, train models to ignore
injected content, or remove injected prompts before execution. StruQ uses
structured queries to separate prompt and data channels~\citep{chen2024struq};
SecAlign uses preference optimization for prompt-injection resistance~\citep{chen2024secalign};
and PromptArmor uses an LLM-based detector/remover as a defense layer~\citep{shi2025promptarmor}.
Recent automated attack work also shows that attack success can depend strongly
on the model and environment~\citep{hofer2026assessing}. Our TraceGate defense is
complementary: it does not try to make the model internally distinguish all
instructions from data. Instead, it enforces a small set of authorization rules
at the tool boundary, following the systems intuition that sensitive side effects
should not rely solely on natural-language compliance.

\section{Limitations}

SLaMBench is synthetic. This makes the results controllable and safe, but it does
not prove attack rates in production systems. The main scaled result is currently
strongest for \texttt{gpt-5.4-nano}; \texttt{gpt-4.1-nano} is a mixed
replication because direct exposure is already vulnerable. The current tasks use
mocked tools and deterministic scoring. Real systems may have richer tool
schemas, partial failures, retries, user confirmations, heterogeneous agents,
stateful memories, and organization-specific policies. The extractive c2x
condition is a stress condition rather than a claim that all production Reader
agents are written this way.

TraceGate is deliberately simple. A production version would need richer
provenance tracking, structured authority metadata, user-confirmation paths,
policy compilation, and task-specific authorization definitions. The current
benchmark also emphasizes unauthorized recipients; future work should include
more state-changing tools, richer memory attacks, cross-organization delegation,
and stronger-model replications. Finally, the current analysis is based on saved
runs rather than repeated stochastic sweeps, so variance across decoding settings
and API model updates remains an important follow-up.

\section{Conclusion}

Source laundering is a security-relevant failure mode in multi-agent LLM systems.
The same untrusted instruction can become more effective when transformed into
an action item by a peer agent. On a scaled multidomain benchmark, extractive
delegation increases unauthorized-recipient sends relative to direct exposure,
while a deterministic tool-boundary monitor eliminates observed unauthorized
sends and preserves injected-task utility. Multi-agent design should treat
inter-agent summaries and plans as untrusted by default unless authority is
explicitly preserved and enforced.

\section*{Ethics Statement}

All experiments are conducted in a closed mock environment with synthetic data,
synthetic secrets, synthetic recipients, and no external side effects. The release
package is limited to synthetic tasks, mock tools, aggregate logs, and
deterministic scoring scripts, with no live targets or real credentials. The
benchmark is intended to support defensive evaluation of provenance-preserving
agent designs and tool-boundary authorization checks.

\bibliographystyle{colm2026_conference}
\bibliography{refs}

\end{document}
